---
title: "Project 4 - Paper 5: C/E/Mr"
author: Team 8
date: "4/14/2017"
output: html_notebook
---

In this notebook, we focus on the method mentioned in the paper written by Song, Yang, et al. for the name disambiguation issue. We adopted Clusterwise Score Function, and used Error-Driven Online Training to generate examples and Ranking MIRA as the loss function.

## Step 0: Load the packages, specify directories
```{r}
#setwd("~/Project4_WhoIsWho/doc")
if (!require("pacman")) install.packages("pacman")
pacman::p_load(text2vec, dplyr, qlcMatrix, kernlab, knitr)
library(stringr)
library(qlcMatrix)
```

## Step 1: Data & Feature Preparation

The features used for our experiments are as follows. We use the attributes of co-authors, paper titles and journals provided in the nameset folder. After comparing different similarity measures, we use TF-IDF measure to calculate similarity. Before that, we construct a document-term matrix (DTM).
```{r}
load("../output/dtm_list.RData")
load("../output/tfidf_list.RData")
dtm_train_tfidf<-tfidf_list[[1]]$tfidf
label<-rownames(as.data.frame(as.matrix(dtm_list[[1]]$dtm)))
```

## Step 2: Algorithm

### Clustering
We use agglomerative clustering method.
```{r}
lamda<-vector(length=dim(dtm_train_tfidf)[2])

lamda<-rep(1,dim(dtm_train_tfidf)[2])

L<- rep(lamda,each=dim(dtm_train_tfidf)[1])
L<- matrix(L,nrow = dim(dtm_train_tfidf)[1], ncol = dim(dtm_train_tfidf)[2])

dtm_train_tfidf<-dtm_train_tfidf*L 
docsdissim <- cosSparse(t(dtm_train_tfidf))
rownames(docsdissim) <- c(1:nrow(dtm_train_tfidf))
colnames(docsdissim) <- c(1:nrow(dtm_train_tfidf))

h <- hclust(as.dist(docsdissim), method = "ward.D")
```

### Clusterwise Scoring Function
We define the clusterwise scoring function as the sum of scores for each cluster.
```{r}
s<-NULL
Score<-function(lamda,result_hclust){
  f<-matrix(NA,nrow=dim(dtm_train_tfidf)[2],ncol=length(unique(result_hclust)))
  for (i in 1:length(unique(result_hclust))){
       
       cluster<-unique(result_hclust)
       num<-count[result_hclust == cluster[i]]
       
       if (length(num) > 1){
       f[,i]<-colMeans(dtm_train_tfidf[num,])
       }
       else{
       f[,i]<-dtm_train_tfidf[num,]
       }
        
       s[i]<-t(lamda) %*% f[,i]
   }
  S<-sum(s)
  return(S)
}
```

### CreateExamplesFromErrors by Error-driven Online Training
We employ a sampling scheme that selects training examples based on errors that occur during inference on the labeled training data (Culotta, Aron, et al., 2007).
```{r}
source('../lib/evaluation_measures.R')
count<-1:length(label)
M<-length(label)
K<-(M-1):2
acc<-NULL
sco<-NULL
neighbor<-matrix(NA, nrow = length(label),ncol = 100)
best<-matrix(NA, nrow = length(label), ncol = 2)

errordriven<-function(h){
for (m in 1:(M-2)){
   k<-K[m]
     result_hclust <- cutree(h,k)
     for (i in 1:k){
       num<-count[result_hclust == i]
       if (length(unique(label[num]))>1)
        { 
         for (j in 1:100){
         neighbor[,j]<-sample(1:k,length(label),replace  = T)
         matching_matrix_hclust <- matching_matrix(label,neighbor[,j])
         acc[j] <- performance_statistics(matching_matrix_hclust)[[1]]
         sco[j]<-Score(lamda,neighbor[,j])
         }
       }
     }
        best[,1]<-neighbor[,which.max(acc)]
        best[,2]<-neighbor[,which.max(sco)]
 }
  return(best)
}
```

### UpdateParameters by Ranking MIRA
We use a variant of MIRA (Mar- gin Infused Relaxed Algorithm), a relaxed, online max- imum margin training algorithm (Crammer & Singer 2003). As discussed in the paper, We updates the parameter vector with three constraints: (1) the better neighbor must have a higher score by a given margin, (2) the change to Λ should be minimal, and (3) the inferior neighbor must have a score below a user-defined threshold (Culotta, Aron, et al., 2007).
```{r}
s1<-NULL
s2<-NULL

UpdateMatrix<-function(result_hclust){
  
  for (i in 1:length(unique(result_hclust))){
       
       cluster<-unique(result_hclust)
       num<-count[result_hclust == cluster[i]]
       
       if (length(num) > 1){
       f[,i]<-colMeans(dtm_train_tfidf[num,],na.rm = T)
       }
       else{
       f[,i]<-dtm_train_tfidf[num,]
       }
   }
       ff<-colMeans(t(f),na.rm = T)
       return(ff)
}


fr <- function(x){
  sum((x-lamda)^2)
}
```

### Whole Algorithm
```{r}
lamda<-rep(1,dim(dtm_train_tfidf)[2])
margin<-0.01
tao<--30

LAMDA <- matrix (NA,nrow = length(lamda),ncol = 2)
LAMDA[,1] <- lamda

for (p in 1:100){

# The feature matrix after weighed by parameters
L<- rep(LAMDA[p],each=dim(dtm_train_tfidf)[1])
L<- matrix(L,nrow = dim(dtm_train_tfidf)[1], ncol = dim(dtm_train_tfidf)[2])
dtm_train_tfidf<-dtm_train_tfidf*L 
docsdissim <- cosSparse(t(dtm_train_tfidf))
rownames(docsdissim) <- c(1:nrow(dtm_train_tfidf))
colnames(docsdissim) <- c(1:nrow(dtm_train_tfidf))

# Cluster based on the feature matrix
h <- hclust(as.dist(docsdissim), method = "ward.D")

# Drive the error
best<-errordriven(h)

# Update the parameters
f1<-UpdateMatrix(best[,1])
f2<-UpdateMatrix(best[,2])
f3<-f1-f2
u1<-rbind(f3,-f2)
c1<-c(margin,tao)

fr <- function(x){
  sum((x-LAMDA[p])^2)
}

optim<-constrOptim(LAMDA[p],fr,grad = NULL, ui = u1,ci = c1)
lamda<-optim$par
LAMDA<-cbind(LAMDA,lamda)

# Converage
if (sum((LAMDA[p+1]-LAMDA[p])^2)<0.1)
{
  break
}
}

```

### Result Cluster
```{r}
lamdaoptim<-LAMDA[,dim(LAMDA)[2]]
L<- rep(lamdaoptim,each=dim(dtm_train_tfidf)[1])
L<- matrix(L,nrow = dim(dtm_train_tfidf)[1], ncol = dim(dtm_train_tfidf)[2])

dtm_train_tfidf<-dtm_train_tfidf*L 
docsdissim <- cosSparse(t(dtm_train_tfidf))
rownames(docsdissim) <- c(1:nrow(dtm_train_tfidf))
colnames(docsdissim) <- c(1:nrow(dtm_train_tfidf))

h <- hclust(as.dist(docsdissim), method = "ward.D")

result_hclust <- cutree(h,k)
```

Other data we use
```{r}
# After we calculate the parameters, we can employ it on the other 9 files and can average the paramters. Then we can test on the other 4 files.
```

## Step 3: Evaluation

For evaluation, we use the standard "Precision", "Recall","F1", and "Accuracy" defined as follows.
$$
\begin{aligned}
\mbox{Precision} &=\frac{a}{a+b}\\
\mbox{Recall}&=\frac{a}{a+c}\\
\mbox{F1} &=\frac{2\times\mbox{Precision}\times\mbox{Recall}}{\mbox{Precision}+\mbox{Recall}}\\
\mbox{Accuracy}&=\frac{a+d}{a+b+c+d}
\end{aligned}
$$
```{r}
source('../lib/evaluation_measures.R')
matching_matrix_hclust <- matching_matrix(label,result_hclust)
performance_hclust <- performance_statistics(matching_matrix_hclust)
df <- data.frame(precision=performance_hclust$precision,
recall=performance_hclust$recall,
f1=performance_hclust$f1,
accuracy=performance_hclust$accuracy,
time=c(time_hclust))
```